---
title: "Final Analysis"
author: "Om Mehta"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
set.seed(0)
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(corrplot)
library(caret)
```

## Loading the dataset

```{r}
df <- read.csv("boston-housing-dataset.csv")
df <- df[, -1]
n <- nrow(df)
```

## dropping B

```{r, echo = FALSE}
df <- df[, -12]
```

### Part 2: Log-transformation of CRIM
```{r prelim2, echo = FALSE}
mod_prelim_2 <- lm(MEDV ~ CRIM, data = df)
predicted_prelim_2 <- data.frame(MEDV_PRED = predict(mod_prelim_2, df), CRIM = df$CRIM)
qplot(df$CRIM, df$MEDV) + stat_smooth() + geom_line(data = predicted_prelim_2, aes(x=CRIM, y=MEDV_PRED))
summary(mod_prelim_2)
```

We notice the following:

* the relationship between MEDV and CRIM appears to be an inverse relationship of the form $y = \frac{k}{x}$

* there are too many points with high CRIM values
```{r prelim2_highCRIM, echo = FALSE}
100*sum(df$CRIM <= 5)/n
```

* $R^2$ is very low - the model doesn't fit well
```{r prelim2_r_squared, echo = FALSE}
summary(mod_prelim_2)$adj.r.squared
```
* the residuals do not have mean zero, constant variance, and are not normally distributed,
```{r prelim2_residuals, echo = FALSE}
epsilon_mod_prelim_2 <- mod_prelim_2$residuals
plot(df$CRIM, epsilon_mod_prelim_2)
abline(h = 0, lty = 2)
qqnorm(epsilon_mod_prelim_2)
qqline(epsilon_mod_prelim_2)
```

We deal with this problem by utilizing log(CRIM) instead of CRIM. This displays
a somewhat more linear trend.

```{r prelim2_transformCRIM, echo = FALSE}
df$logCRIM <- log(df$CRIM)
mod_prelim_2_new <- lm(MEDV ~ logCRIM, data = df)
plot(df$logCRIM, df$MEDV)
abline(a = mod_prelim_2_new$coefficients[1], b = mod_prelim_2_new$coefficients[2], lty = 2)
summary(mod_prelim_2_new)
```

## transforming variables

```{r, echo = FALSE}
df$logINDUS <- log(df$INDUS)
df$RAD.t <- ifelse(df$RAD == 24, 1, 0)
df$logDIS <- log(df$DIS)
df$logLSTAT <- log(df$LSTAT)
```

## HIST of MEDV
```{r, echo = FALSE}
hist(df$MEDV, main = "Histogram of MEDV", xlab = "MEDV")
```
##Summary df
```{r}
df_mod <- df[, -1][, -2][, -6][, -9][, -3][, -5][, -8]
summary(df_mod)
sum(df$CHAS == 1)
sum(df$CHAS == 0)
sum(df$RAD.t == 1)
sum(df$RAD.t == 0)
corrplot(cor(df_mod))
```

##Model
```{r}
mod <- lm(MEDV ~ .-CRIM -INDUS - DIS - LSTAT - RAD - NOX - logCRIM, data = df)
summary(mod)
mod_R2 <- summary(mod)$adj.r.squared
epsilon_mod <- mod$residuals
hist(epsilon_mod)
boxplot(epsilon_mod)
qqnorm(epsilon_mod)
qqline(epsilon_mod)
plot(mod$fitted.values,epsilon_mod)
abline(h = 0, lty = 2)
```